Summer Peaks and Winter Lows: An Analysis of Toronto Island Ferry Ticket Counts

### 2024-09-27 Paper/Paper.qmd
updated 'thanks' message in top matter to add the new repo link

---
title: "Summer Peaks and Winter Lows: An Analysis of Toronto Island Ferry Ticket Counts"
subtitle: "What Six Years of Data Reveal About Ferry Usage, Visitor Patterns, and Seasonal Consumer Behaviour"
author: Krishna Kumar
thanks: "Code and data are available at: https://github.com/krishnak30/Toronto-Island-Ferry-Ticket-Counts-Krishna-K.git."
date: today
date-format: long
abstract: "This report examines ferry services to the Toronto Islands, a key recreational area accessible only by water. We analyzed ferry ticket data from May 2018 to September 2024 to uncover patterns in usage, visitor trends, and the impact of external factors like the COVID-19 pandemic. The results show clear seasonal patterns, with significant/unprecedented declines in ferry usage during the pandemic. Our findings emphasize how sensitive ferry services are to seasonal changes and unexpected disruptions, with broader implications for tourism, local economies, urban planning, and the resilience of public transportation systems in response to external shocks."
format: pdf
number-sections: true
bibliography: references.bib
execute:
  echo: false     # Hide code globally
  warning: false  # Suppress warnings globally
  message: false  # Suppress messages globally
references: true
fig-align: center 
---

>>>>

---
title: "Summer Peaks and Winter Lows: An Analysis of Toronto Island Ferry Ticket Counts"
subtitle: "What Six Years of Data Reveal About Ferry Usage, Visitor Patterns, and Seasonal Consumer Behaviour"
author: Krishna Kumar
thanks: "Code and data are available at: https://github.com/krishnak30/Toronto_Islands_Ferry_Ticket_Counts.git"
date: today
date-format: long
abstract: "This report examines ferry services to the Toronto Islands, a key recreational area accessible only by water. We analyzed ferry ticket data from May 2018 to September 2024 to uncover patterns in usage, visitor trends, and the impact of external factors like the COVID-19 pandemic. The results show clear seasonal patterns, with significant/unprecedented declines in ferry usage during the pandemic. Our findings emphasize how sensitive ferry services are to seasonal changes and unexpected disruptions, with broader implications for tourism, local economies, urban planning, and the resilience of public transportation systems in response to external shocks."
format: pdf
number-sections: true
bibliography: references.bib
execute:
  echo: false     # Hide code globally
  warning: false  # Suppress warnings globally
  message: false  # Suppress messages globally
references: true
fig-align: center 
---
